Modeling potential JCPOA breakout scenarios using Cyclus

### 2018-01-27 paper.tex
title draft some light change

\documentclass{anstrans}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{An Improved ANS Transaction Template}
\author{Baptiste Mouginot,$^{*}$ Kathryn Mummah,$^{*}$ Paul P.H. Wilson$^{*}$}

@@

\subsection{Explored Cases}
\subsubsection{Reference Case}

@@

\subsubsection{Case 1}

@@

\subsubsection{Case 2}

@@

Despite the reconfiguration of each level occurring in the second case, the case
1 is notably more effective in producing HEU than case 1. Indeed, as observed in
Figure \ref{fig:assay_c1_rc} and \ref{fig:assay_c2_rc}, the first case is able
to produce an uranium product enrich at $98\%$ while the second case is only
able to reach an enrichment of $88.3\%$ with the same number of levels.

\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
  \centering
  \includegraphics[width=0.5\textwidth]{assay_case_1_no_rec.png}
  \caption{Evolution of the different product assays at each cascade level for
  the case 1 without recycling. The blue line represents the $90\%$ enrichment
  threshold.}\label{fig:assay_c1_nr}
\end{figure}
\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
  \centering
  \includegraphics[width=0.5\textwidth]{assay_case_2_no_rec.png}
  \caption{Evolution of the different product assays at each cascade level for
  the case 2 without recycling. }\label{fig:assay_c2_nr}
\end{figure}

Because the cut value $\theta_i$ at each stage is unchanged, case 2 artificially
produces over-enriched tails when fed with higher enriched materials compared
to a cascade feed with the same feed assay but with a cascade designed for it.

@@

\begin{table}[htb]
\centering
\begin{tabular}{cll}
\toprule

@@

\bottomrule
\end{tabular}
  \caption{Cascade effective $\theta$ by the level and case.}
  \label{tab:cascade_theta}
\end{table}
As illustrated in Table \ref{tab:cascade_theta}, the effective cut
of each level increases up to $0.54$ for the fifth stage for case 2. The high
effective cut value increase the product production rate but decrease the
enrichment ratio.

@@

\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
  \centering
  \includegraphics[width=0.5\textwidth]{HEU_prod.png}
  \caption{Evolution of the amount of HEU in the storage. The blue line
      correspond to one significant quantity of HEU ($25~$kg). CX correpsonds to
      the case number(1 or 2), RT and NRT the tail reprocessing or not ones.
      W/X/Y/Z represent the number of cascade per level. REF corresponds to the
      reference case.}\label{fig:heu_prod}
\end{figure}

It is also interresting to note that despite requiering more level of cascade to
reach an enrichment of $90\%$ the second case with tial recycling produces HEU
at a equivalent rate than the case 1. The production rate seems to be faster but
require more time to reach the maximum production rate (the material have to
flow through more levels to reach the final level).

>>>>

\documentclass{anstrans}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{Modeling potential JCPOA breakout scenarios using Cyclus}
\author{Baptiste Mouginot,$^{*}$ Kathryn Mummah,$^{*}$ Paul P.H. Wilson$^{*}$}

@@

\subsection{Explored Cases}
%\subsubsection{Reference Case}

@@

%\subsubsection{Case 1}

@@

%\subsubsection{Case 2}

@@

\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
  \centering
  \includegraphics[width=0.5\textwidth]{assay_case_1_no_rec.png}
  \caption{Evolution of the different product assays at each cascade level for
  the case 1 without recycling. The blue line represents the $90\%$ enrichment
  threshold.}\label{fig:assay_c1_nr}
\end{figure}
Despite the reconfiguration of each level occurring in the second case, the case
1 is notably more effective in producing HEU than case 1. Indeed, as observed in
Figure \ref{fig:assay_c1_rc} and \ref{fig:assay_c2_rc}, the first case is able
to produce an uranium product enrich at $98\%$ while the second case is only
able to reach an enrichment of $88.3\%$ with the same number of levels.

Because the cut value $\theta_i$ at each stage is unchanged, case 2 artificially
produces over-enriched tails when fed with higher enriched materials compared
to a cascade feed with the same feed assay but with a cascade designed for it.
\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
  \centering
  \includegraphics[width=0.5\textwidth]{assay_case_2_no_rec.png}
  \caption{Evolution of the different product assays at each cascade level for
  the case 2 without recycling. }\label{fig:assay_c2_nr}
\end{figure}

@@

As illustrated in Table \ref{tab:cascade_theta}, the effective cut
of each level increases up to $0.54$ for the fifth stage for case 2. The high
effective cut value increase the product production rate but decrease the
enrichment ratio.
\begin{table}[htb]
\centering
\begin{tabular}{cll}
\toprule

@@

\bottomrule
\end{tabular}
  \caption{Cascade effective $\theta$ by the level and case.}
  \label{tab:cascade_theta}
\end{table}

@@

\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
  \centering
  \includegraphics[width=0.5\textwidth]{HEU_prod.png} \caption{Evolution of the
  amount of HEU in the storage. The blue line correspond to 1 SQ of HEU
  ($25~$kg). Cx, RT(NRT) represents the different cases with (no)tail recycling
  with the cascade population per level and REF the reference
  case.}\label{fig:heu_prod}
\end{figure}

It is also interesting to note that despite requiring more level of cascade to
reach an enrichment of $90\%$ the second case with tail recycling produces HEU
at a equivalent rate than the case 1. The production rate seems to be faster but
require more time to reach the maximum production rate (the material have to
flow through more levels to reach the final level).
